---
title: "Penguins EDA"
format:
  html:
    code-fold: true
---

In this section, we explore some cool functionalites in R!

Here, we load the required libraries and connect to the DuckDB dataset to store it onto memory.

```{r message=FALSE,warning=FALSE}
library(palmerpenguins)
library(dplyr)
library(ggplot2)
library(dbplyr)
library(knitr)
library(rmarkdown)

con <- DBI::dbConnect(
  duckdb::duckdb(), 
  dbdir = "my-db.duckdb"
  )
df <- dplyr::tbl(con, "penguins")
```

Next, we clean the pulled data and organize it in a table. The snippet below gives us an idea of the parameters within each data frame.

```{r message=FALSE,warning=FALSE}
## Penguin Size and Mass by Sex and Species

df %>%
  group_by(species, sex) %>%
  summarise(
    across(
        ends_with("mm") | ends_with("g"),
      \(x) mean(x, na.rm = TRUE)
      )
    ) %>%
  dplyr::collect() %>%
  knitr::kable()

```

To further visualize the data, the graph below plots body mass in grams vs bill length in millimeters, which each species separated by a different color.

```{r message=FALSE,warning=FALSE}
## Penguin Size vs Mass by Species

df %>%
  ggplot(aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  geom_point() + 
  geom_smooth(method = "lm")
```

Lastly, we safely shut down the connection.

```{r message=FALSE,warning=FALSE}
DBI::dbDisconnect(con, shutdown = TRUE)
```
